---
title: "Simple Linear Regression using Rcpp"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SimpLin}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SimpLin)
```

# Purpose

This package is designed to perform simple linear regression in Rcpp given any predictor variable `x` and response variable `y`. 

# Functionality

The `SimpLin` package contains 2 functions: `SimpLinCpp`, which runs a simple linear regression model in the C++ framework, and `SimpLinR`, an R wrapper function that catches errors. Only `SimpLinR` should be run by the user. 

`SimpLinR` takes two arguments, both of which should be numeric vectors. The first is the predictor variable and the second is the response variable.

```{r eval=FALSE}
x = runif(10)
y = rnorm(10, mean=(3+5*x))

SimpLinR(x, y)
```

The function will output a list containing the estimated $\beta$ coefficients, their standard errors and 95% confidence intervals, residuals, and predicted (fitted) values. If wrong input is given, `SimpLinR` will output an error. 

```{r echo=FALSE}
x = runif(10)
y = rnorm(10, mean=(3+5*x))

SimpLinR(x,y)
```







